Reflections from reproductions

### 2024-11-04 pages/reflections.qmd
docs(reflections): moved excess files to other

<!--TODO: Move this to other, or move things from other up here into their own boxes -->

## Do not output excessive numbers of files

I have not evaluated this as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.

Regarding number of files:

* @shoaib_simulation_2021: Not relevant.
* @huang_optimizing_2019: Not relevant.
* @lim_staff_2020: Not relevant.
* @kim_modelling_2021: Not relevant.
* @anagnostou_facs-charm_2022: Not relevant.
* @johnson_cost_2021: Not relevant.
* @hernandez_optimal_2015: The default behaviour of the script was to output **lots of files** from each round (so you could easily have 90, 100, 200+ files), which were then **not** used in analysis (as it just depended on an aggregate results file). Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
* @wood_value_2021: Not relevant.

* Outputting hundreds of files - particularly if they are not then used normally in analysis - can easily make repository cluttered/busy

@@

>>>>

@@

**Excessive number of files**. For @hernandez_optimal_2015 the default behaviour of the script was to output lots of files from each round (so you could easily have 90, 100, 200+ files), which were then not used in analysis (as it just depended on an aggregate results file). Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
